Hierarchically modelling \emph{Kepler} dwarfs and subgiants to improve inference of stellar properties with asteroseismology

### 2021-02-03 paper/main.tex
Updated acknowledgements

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[A. J. Lyttle et al.]{%
Alexander J. Lyttle,$^{1,2}$\thanks{E-mail: ajl573@student.bham.ac.uk}
Guy R. Davies,$^{1,2}$
Tanda Li,$^{1,2}$
Lindsey M. Carboneau,$^{1,2}$
\newauthor
Hin Leung,$^{1,2,3}$
Harry Westwood,$^{1,2}$
William J. Chaplin,$^{1,2}$
Oliver J. Hall,$^{4,1,2}$
\newauthor
Daniel Huber,$^{5}$
Andrea Miglio,$^{1,2}$
Martin B. Nielsen,$^{1,2}$
Sarbani Basu,$^{6}$
\newauthor
Will M. Farr,$^{7,8}$
and Rafael A. Garc\'ia$^{9}$
\\
% List of institutions
$^{1}$School of Physics and Astronomy, University of Birmingham, Birmingham, B15 2TT, UK\\
$^{2}$Stellar Astrophysics Centre (SAC), Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
$^{3}$School of Physics and Astronomy, University of St Andrews, North Haugh, St Andrews, KY16 9SS, UK\\
$^{4}$European Space Agency (ESA), European Space Research and Technology Centre (ESTEC), Keplerlaan 1, 2201 AZ Noordwijk, Netherlands\\
$^{5}$Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
$^{6}$Department of Astronomy, Yale University, 52 Hillhouse Avenue, New Haven, CT 06511, USA\\
$^{7}$Center for Computational Astrophysics, Flatiron Institute, 162 5th Avenue, New York, New York 10010, USA\\
$^{8}$Department of Physics and Astronomy, Stony Brook University, Stony Brook, New York 11794, USA\\
$^{9}$AIM, CEA, CNRS, Universit\'e Paris-Saclay, Universit\'e Paris Diderot, Sorbonne Paris Cit\'e, 91191, Gif-sur-Yvette, France\\
}

@@

This work is a part of a project that has received funding from the European Research Council (ERC) under the European Union’s Horizon 2020 research and innovation programme (CartographY; grant agreement ID 804752). We thank Ilya Mandel and Sean Matt for their discussion regarding this work. D.H. acknowledges support from the Alfred P. Sloan Foundation, the National Aeronautics and Space Administration (80NSSC19K0597), and the National Science Foundation (AST-1717000). R.A.G acknowledges the funding from the PLATO CNES grant.

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[A. J. Lyttle et al.]{%
Alexander J. Lyttle,$^{1,2}$\thanks{E-mail: ajl573@student.bham.ac.uk}
Guy R. Davies,$^{1,2}$
Tanda Li,$^{1,2}$
Lindsey M. Carboneau,$^{1,2}$
\newauthor
Hin Leung,$^{1,2,3}$
Harry Westwood,$^{1,2}$
William J. Chaplin,$^{1,2}$
Oliver J. Hall,$^{4,1,2}$
\newauthor
Daniel Huber,$^{5}$
Andrea Miglio,$^{1,2}$
Martin B. Nielsen,$^{1,2,6}$
Sarbani Basu,$^{7}$
\newauthor
Will M. Farr,$^{8,9}$
and Rafael A. Garc\'ia$^{10}$
\\
% List of institutions
$^{1}$School of Physics and Astronomy, University of Birmingham, Birmingham, B15 2TT, UK\\
$^{2}$Stellar Astrophysics Centre (SAC), Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
$^{3}$School of Physics and Astronomy, University of St Andrews, North Haugh, St Andrews, KY16 9SS, UK\\
$^{4}$European Space Agency (ESA), European Space Research and Technology Centre (ESTEC), Keplerlaan 1, 2201 AZ Noordwijk, Netherlands\\
$^{5}$Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
$^{6}$Center for Space Science, NYUAD Institute, New York University Abu Dhabi, PO Box 129188, Abu Dhabi, United Arab Emirates\\
$^{7}$Department of Astronomy, Yale University, 52 Hillhouse Avenue, New Haven, CT 06511, USA\\
$^{8}$Center for Computational Astrophysics, Flatiron Institute, 162 5th Avenue, New York, New York 10010, USA\\
$^{9}$Department of Physics and Astronomy, Stony Brook University, Stony Brook, New York 11794, USA\\
$^{10}$AIM, CEA, CNRS, Universit\'e Paris-Saclay, Universit\'e Paris Diderot, Sorbonne Paris Cit\'e, 91191, Gif-sur-Yvette, France\\
}

@@

This work is a part of a project that has received funding from the European Research Council (ERC) under the European Union’s Horizon 2020 research and innovation programme (CartographY; grant agreement ID 804752). A.J.L., G.R.D.,  and W.J.C. acknowledge the support of the Science and Technology Facilities Council. D.H. acknowledges support from the Alfred P. Sloan Foundation, the National Aeronautics and Space Administration (80NSSC19K0597), and the National Science Foundation (AST-1717000). M.B.N. acknowledges support from the UK Space Agency. R.A.G. acknowledges the funding from the PLATO CNES grant. We thank Ilya Mandel and Sean Matt for their discussion regarding this work.
